---
title: "Demo with chart"
author: "Kyle Thayer"
format:
  html:
    embed-resources: true
editor: visual
---

## Step 1: Load libraries
*Note: I am going to hide the code that loads libraries, and I will ignore warnings*
```{r}
#| warnings: false
#| include: false

# I will be using dplyr and ggplot2
library("dplyr")
library("ggplot2")

```

## Step 1b: Load student data
```{r}
# Load fake student data
fake_student_df <- read.csv("https://raw.githubusercontent.com/kylethayer/Info-201-au-24-datasets/refs/heads/main/demo_L03_fake_students.csv")
```


## Step 2: Show student ages
```{r}
ggplot(fake_student_df) +
  geom_col(mapping = aes(x = student_num, y = age))

```
## Step 2b: Info about students
```{r}
avg_age <- fake_student_df |>
    pull(age) |>
    mean(na.rm = TRUE)

```
The average age of students (who we have age data for) is `r avg_age`. 


## Step 3: Age vs. Final exam score
```{r}
ggplot(fake_student_df) +
  geom_point(mapping = aes(x = age, y = final_exam_score))

```

## Step 4: Make a chart with the midwest demo dataset
*Note: I think you might need a different code chunk for each chart display, but I'm not sure*
```{r}
ggplot(midwest) +
  geom_point(mapping = aes(
    x = percollege,
    y = percadultpoverty
  ))

```

