--- 
title: "Fire Response Demo Dashboard"
author: "Carson G Miller Rigoli"
format: 
  html:
    theme: simplex
    embed-resources: true
---

```{r}
#| output: false

#install.packages("plotly")
#install.packages("DT")
library(tidyverse)
library(plotly)
library(DT)

calls <- read.csv("https://data.seattle.gov/resource/kzjm-xkqj.csv")
#calls <- read.csv("calls.csv")
```

# Call Types 

Call types may not be consistently labeled. Be sure to check the full list of recorded types.

```{r}
calls |> ggplot(aes(y = type)) + geom_bar()
```


```{r}
calls |> glimpse()
```


# Call Locations 

Double click on call types to filter by type in the visualization. Single click to remove a type.

```{r}
plot1 <- calls |>
  ggplot(aes(x = longitude, y = latitude)) +
  geom_point() +
  geom_text(label = "UW", x = -122.3066, y = 47.6567, color = "red", shape = "x")+
  geom_text(label = "Pike Place", x = -122.3418, y = 47.6094, color = "red", shape = "x")

plot1 
```

```{r}
calls |> glimpse()
```

# Notes

This dashboard presents data from Seattle City real-time fire response data. Information is available on the [Seattle City Open Data Website](https://data.seattle.gov/Public-Safety/Seattle-Real-Time-Fire-911-Calls/kzjm-xkqj/about_data).

This dashboard was created by Dr. Carson G. Miller Rigoli at the University of Washington.

This dashboard was created for example purposes for INFO 201.

Create notes as you follow along with the notes template at the in-class links accompanying this file.

For more information, check out the Quarto documentation for [dashboards](https://quarto.org/docs/dashboards/layout.html).

